### 2020-03-30 papers.tex
Fix paper title miscapitalization

\addtrack
	{}{Theory}
\addpaper
	{A polynomial-time SAT algorithm}
	{Anonymous Author(s)}
	{Keywords: theoretical computer science, complexity theory, p versus np}
	{SIGBOVIK_2020_paper_2}
	{0cm}
	{}
\addpaper
	{Empire Machines and beyond}
	{Dar\'io de la Fuente Garc\'ia, F\'elix \'Axel Gimeno Gil, Juan Carlos Morales Vega}
	{Keywords: finite-state machines, models of computation, Empire Machines, doing research like this is awesome, Civilization XXIV (when it comes out)}
	{SIGBOVIK_2020_paper_16}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_8}{0cm}
\addpaper
	{Artificial general relativity}
	{Pablo Samuel Castro}
	{Keywords: physics, artificial, general relativity, quantum physics, universe-changing, new science, field equations, black holes}
	{SIGBOVIK_2020_paper_14}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_5}{0cm}
\addpaper
	{Making explicit a constant appearing in an impossible equation of Carl and Moroz}
	{Matthew Weidner}
	{Keywords: computational mathematics, Hilbert's tenth problem, Diophantine sets}
	{SIGBOVIK_2020_paper_8}
	{0cm}
	{}

>>>>

\addtrack
	{}{Theory}
\addpaper
	{A polynomial-time SAT algorithm}
	{Anonymous Author(s)}
	{Keywords: theoretical computer science, complexity theory, p versus np}
	{SIGBOVIK_2020_paper_2}
	{0cm}
	{}
\addpaper
	{Empire Machines and beyond}
	{Dar\'io de la Fuente Garc\'ia, F\'elix \'Axel Gimeno Gil, Juan Carlos Morales Vega}
	{Keywords: finite-state machines, models of computation, Empire Machines, doing research like this is awesome, Civilization XXIV (when it comes out)}
	{SIGBOVIK_2020_paper_16}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_8}{0cm}
\addpaper
	{Artificial General Relativity}
	{Pablo Samuel Castro}
	{Keywords: physics, artificial, general relativity, quantum physics, universe-changing, new science, field equations, black holes}
	{SIGBOVIK_2020_paper_14}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_5}{0cm}
\addpaper
	{Making explicit a constant appearing in an impossible equation of Carl and Moroz}
	{Matthew Weidner}
	{Keywords: computational mathematics, Hilbert's tenth problem, Diophantine sets}
	{SIGBOVIK_2020_paper_8}
	{0cm}
	{}
